### 2016-08-31 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Final edits to hose stream paper, just need TN # from PR, so hopefully will be published by end of year

\subsubsection{Layout}
\label{sec:layout}
Dimensioned floor plans of the Single Story and Two Story Structures are presented in Fig.~\ref{fig:east_dimensioned_plan} and Fig.~\ref{fig:west_dimensioned_plan}, respectively.

@@

@@

\begin{table}[!ht]
\caption{Average gas velocity and airflow rate [$\pm 18$~\%] through interior doorway when flow path was fully established for Test~5}
\begin{tabular}{lccccc}
\toprule
 &	&	&	\multicolumn{3}{c}{\underline{Room A}}
\\
\textbf{Stream} & \textbf{Value} & \textbf{Units} &
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity}
& 		 \small{m/s}   	&   0.2 $\pm0.03$	&   0.7 $\pm0.1$	&	 0.8 $\pm0.2$  \\ 
&	&	 \small{(mph)} 	&  (0.4 $\pm0.1$)	&  (1.5 $\pm0.3$)	&	(1.9 $\pm0.3$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 0.3 $\pm0.1$	&  1.2 $\pm0.2$		&	 1.6 $\pm0.3$  	\\
& 	&	\small{(cfm)}	& 	(628 $\pm113$)	& (2584 $\pm465$) 	&	(3291 $\pm592$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
& 		\small{m/s}   	&	 1.7 $\pm0.3$   	&	 1.8 $\pm0.3$  	&   1.6 $\pm0.3$   \\
&	&	\small{(mph)} 	&	(3.9 $\pm0.7$) 		&	(4.0 $\pm0.7$) 	&  (3.5 $\pm0.6$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 3.2 $\pm0.6$   	&	 3.3 $\pm0.6$		&	 2.9 $\pm0.5$  	\\
& 	&	\small{(cfm)}	& 	(6786 $\pm1222$)	&	(6977 $\pm1256$) 	&	(6228 $\pm1121$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
&		\small{m/s} 	&	 1.8 $\pm0.3$   	&   2.1 $\pm0.4$  	&   2.2 $\pm0.4$  \\ 
& 	& 	\small{(mph)}	&	(4.1 $\pm0.7$)  	&  (4.8 $\pm0.9$) 	&  (4.9 $\pm0.9$)  
\\ ~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 3.4 $\pm0.6$   	&  4.0 $\pm0.7$		&	 4.1 $\pm0.7$  	\\
& 	&	\small{(cfm)}	& 	(7283 $\pm1311$)	& (8463 $\pm1523$) 	&	(8669 $\pm1561$) \\
\midrule
&	&	&	\multicolumn{3}{c}{\underline{Room B Ceiling}}
\\
\textbf{Stream} & \textbf{Value} & \textbf{Units} &
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity}
& 		 \small{m/s}   	&   -0.1 $\pm0.02$    	&   0.6 $\pm0.1$   	&	 0.5 $\pm0.1$  \\ 
&	&	 \small{(mph)} 	&  (-0.2 $\pm0.04$)  	&  (1.4 $\pm0.3$) 	&	(1.2 $\pm0.2$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 -0.2 $\pm0.03$   	&  1.2 $\pm0.2$		&	 1.0 $\pm0.2$  	\\
& 	&	\small{(cfm)}	& 	(-381 $\pm69$)		& (2469 $\pm445$) 	&	(2155 $\pm388$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
& 		\small{m/s}   	&   0.9 $\pm0.2$   		&   1.5 $\pm0.3$  	&   1.6 $\pm0.3$   \\
&	&	\small{(mph)} 	&  (2.1 $\pm0.4$)  		&  (3.4 $\pm0.6$) 	&  (3.7 $\pm0.7$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 1.8 $\pm0.3$   	&  2.9 $\pm0.5$		&	 3.1 $\pm0.6$  	\\
& 	&	\small{(cfm)}	& 	(3739 $\pm673$)		& (6046 $\pm1088$) 	&	(6479 $\pm1166$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
&		\small{m/s} 	&   2.1 $\pm0.4$   		&   2.3 $\pm0.4$  	&   2.6 $\pm0.5$  \\ 
& 	& 	\small{(mph)}	&  (4.7 $\pm0.8$)  		&  (5.2 $\pm0.9$) 	&  (5.8 $\pm1.1$)  
\\ ~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 3.9 $\pm0.7$   	&  4.3 $\pm0.8$		&	 4.8 $\pm0.9$  	\\
& 	&	\small{(cfm)}	& 	(8271 $\pm1489$)	& (9165 $\pm1650$) 	&	(10273 $\pm1849$) \\
\bottomrule
\end{tabular}
\label{table:east_hand_A6_avgs}
\end{table}

@@

& 	&	\small{(cfm)}	& 	(-670 $\pm121$)		&	(1864 $\pm336$)		&	(2549 $\pm459$)		& 	(2602 $\pm468$)

@@

& 	&	\small{(cfm)}	& 	(1471 $\pm265$)		&	(3688 $\pm664$) 	&	(3034 $\pm546$)		& 	(3786 $\pm682$)

@@

& 	&	\small{(cfm)}	& 	(3369 $\pm606$)		&	(3362 $\pm605$) 	&	(3453 $\pm622$)		& 	(3051 $\pm549$)

@@

& 	&	\small{(cfm)}	& 	(-152 $\pm27$)		&	(1804 $\pm325$) 	&	(2473 $\pm445$)		& 	(2358 $\pm425$)

@@

& 	&	\small{(cfm)}	& 	(4494 $\pm809$)		& 	(4326 $\pm779$) 	&	(4214 $\pm759$)		& 	(4477 $\pm806$)

@@

& 	&	\small{(cfm)}	& 	(3509 $\pm632$)		&	(2503 $\pm451$) 	&	(3299 $\pm594$)		& 	(3428 $\pm617$)

@@

\appendix
\chapter{Monitor Test Plots}
\label{chap:monitor_plots}

>>>>

\subsubsection{Layout}
\label{sec:layout}
Simple floor plans showing the total length and width of the Single Story and Two Story Structures are presented in Fig.~\ref{fig:east_dimensioned_plan} and Fig.~\ref{fig:west_dimensioned_plan}, respectively. Fully dimensioned floor plan drawings are provided in Appendix~\ref{chap:floor_plans}.

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Test_Structure_Dimensioned_LxW}
	\caption[Simple floor plan of the Single Story Structure.]{Simple floor plan of the Single Story Structure.}
	\label{fig:east_dimensioned_plan}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.985\columnwidth]{../Figures/Floor_Plans/West_Test_Structure_2nd_Floor_Dimensioned_LxW}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Test_Structure_1st_Floor_Dimensioned_LxW}
	\caption[Simple floor plan of the first and second floors of the Two Story Structure.]{Simple floor plan of the second floor (top) and first floor (bottom) of the Two Story Structure.}
	\label{fig:west_dimensioned_plan}
\end{figure}

@@

\begin{table}[!ht]
\caption{Average gas velocity and airflow rate [$\pm 18$~\%] through interior doorway when flow path was fully established for Test~5}
\begin{tabular}{lccccc}
\toprule
 &	&	&	\multicolumn{3}{c}{\underline{Room A}}
\\
\textbf{Stream} & \textbf{Value} & \textbf{Units} &
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity}
& 		 \small{m/s}   	&   0.2 $\pm0.03$	&   0.7 $\pm0.1$	&	 0.8 $\pm0.2$  \\ 
&	&	 \small{(mph)} 	&  (0.4 $\pm0.1$)	&  (1.5 $\pm0.3$)	&	(1.9 $\pm0.3$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 0.3 $\pm0.1$	&  1.2 $\pm0.2$		&	 1.6 $\pm0.3$  	\\
& 	&	\small{(cfm)}	& 	(650 $\pm100$)	& (2600 $\pm450$) 	&	(3300 $\pm600$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
& 		\small{m/s}   	&	 1.7 $\pm0.3$   	&	 1.8 $\pm0.3$  	&   1.6 $\pm0.3$   \\
&	&	\small{(mph)} 	&	(3.9 $\pm0.7$) 		&	(4.0 $\pm0.7$) 	&  (3.5 $\pm0.6$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 3.2 $\pm0.6$   	&	 3.3 $\pm0.6$		&	 2.9 $\pm0.5$  	\\
& 	&	\small{(cfm)}	& 	(6800 $\pm1200$)	&	(7000 $\pm1250$) 	&	(6250 $\pm1100$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
&		\small{m/s} 	&	 1.8 $\pm0.3$   	&   2.1 $\pm0.4$  	&   2.2 $\pm0.4$  \\ 
& 	& 	\small{(mph)}	&	(4.1 $\pm0.7$)  	&  (4.8 $\pm0.9$) 	&  (4.9 $\pm0.9$)  
\\ ~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 3.4 $\pm0.6$   	&  4.0 $\pm0.7$		&	 4.1 $\pm0.7$  	\\
& 	&	\small{(cfm)}	& 	(7300 $\pm1300$)	& (8450 $\pm1500$) 	&	(8650 $\pm1550$) \\
\midrule
&	&	&	\multicolumn{3}{c}{\underline{Room B Ceiling}}
\\
\textbf{Stream} & \textbf{Value} & \textbf{Units} &
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity}
& 		 \small{m/s}   	&   -0.1 $\pm0.02$    	&   0.6 $\pm0.1$   	&	 0.5 $\pm0.1$  \\ 
&	&	 \small{(mph)} 	&  (-0.2 $\pm0.04$)  	&  (1.4 $\pm0.3$) 	&	(1.2 $\pm0.2$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 -0.2 $\pm0.03$   	&  1.2 $\pm0.2$		&	 1.0 $\pm0.2$  	\\
& 	&	\small{(cfm)}	& 	(-400 $\pm50$)		& (2450 $\pm450$) 	&	(2150 $\pm400$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
& 		\small{m/s}   	&   0.9 $\pm0.2$   		&   1.5 $\pm0.3$  	&   1.6 $\pm0.3$   \\
&	&	\small{(mph)} 	&  (2.1 $\pm0.4$)  		&  (3.4 $\pm0.6$) 	&  (3.7 $\pm0.7$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 1.8 $\pm0.3$   	&  2.9 $\pm0.5$		&	 3.1 $\pm0.6$  	\\
& 	&	\small{(cfm)}	& 	(3750 $\pm650$)		& (6050 $\pm1100$) 	&	(6500 $\pm1150$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
&		\small{m/s} 	&   2.1 $\pm0.4$   		&   2.3 $\pm0.4$  	&   2.6 $\pm0.5$  \\ 
& 	& 	\small{(mph)}	&  (4.7 $\pm0.8$)  		&  (5.2 $\pm0.9$) 	&  (5.8 $\pm1.1$)  
\\ ~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 3.9 $\pm0.7$   	&  4.3 $\pm0.8$		&	 4.8 $\pm0.9$  	\\
& 	&	\small{(cfm)}	& 	(8250 $\pm1500$)	& (9150 $\pm1650$) 	&	(10250 $\pm1850$) \\
\bottomrule
\end{tabular}
\label{table:east_hand_A6_avgs}
\end{table}

@@

& 	&	\small{(cfm)}	& 	(-650 $\pm100$)		&	(1850 $\pm350$)		&	(2550 $\pm450$)		& 	(2600 $\pm450$)

@@

& 	&	\small{(cfm)}	& 	(1450 $\pm250$)		&	(3700 $\pm650$) 	&	(3050 $\pm550$)		& 	(3800 $\pm700$)

@@

& 	&	\small{(cfm)}	& 	(3350 $\pm600$)		&	(3350 $\pm600$) 	&	(3450 $\pm600$)		& 	(3050 $\pm550$)

@@

& 	&	\small{(cfm)}	& 	(-150 $\pm50$)		&	(1800 $\pm300$) 	&	(2450 $\pm450$)		& 	(2350 $\pm400$)

@@

& 	&	\small{(cfm)}	& 	(4500 $\pm800$)		& 	(4350 $\pm800$) 	&	(4200 $\pm750$)		& 	(4500 $\pm800$)

@@

& 	&	\small{(cfm)}	& 	(3500 $\pm650$)		&	(2500 $\pm450$) 	&	(3300 $\pm600$)		& 	(3450 $\pm600$)

@@

\appendix
\chapter{Fully Dimensioned Floor Plans}
\label{chap:floor_plans}

\chapter{Monitor Test Plots}
\label{chap:monitor_plots}
